To Do List

### 2019-11-07 Papers.Rmd
Add themis
Add Prati 2009 review

@@

@@

>>>>

- Schreiber, Jacob, Maxwell Libbrecht, Jeffrey Bilmes, and William Stafford Noble. “Nucleotide Sequence and DNaseI Sensitivity Are Predictive of 3D Chromatin Architecture.” Preprint. Bioinformatics, January 27, 2017. https://doi.org/10.1101/103614. - Rambutan - a deep convolutional network predicting Hi-C contacts from DNA sequence (one-hot encoded) and DHSs (signal, logFC over control). Fit-Hi-C defines significant (q-value <= 1e-6) contacts used for training. Genomic distance (binarized) is also included. 1kb-5kb data. AUROC, AUPR for performance evaluation.Description of network topology, training. Balanced batches for training. Predictions correlated with Insulation Score, replication timing. Predict Hi-C contacts for 53 human cell types, clustered by cell types. https://github.com/jmschrei/rambutan

@@

- Prati, Ronaldo C, Gustavo EAPA Batista, and Maria Carolina Monard. “Data Mining with Imbalanced Class Distributions: Concepts and Methods.” In IICAI, 359–376, 2009.
. Class imbalance problem, methods to address it. From ROS/RUS to heuristic ROS/RUS, cost-sensitive learning. Metrics for evaluation.

@@

- Extra recipes steps for dealing with unbalanced data. https://github.com/EmilHvitfeldt/themis
